Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-31 paper/manuscript.Rmd
update figure / fix floating pointst
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Neither the main effect of Articulation (*F*(`r ftop_all_aov$anova_table[1,1]`, `r ftop_all_aov$anova_table[1,2]`) = `r ftop_all_aov$anova_table[1,4]`, *p* `r if(ftop_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ftop_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[1,5])`) nor Dynamics (*F*(`r ftop_all_aov$anova_table[2,1]`, `r ftop_all_aov$anova_table[2,2]`) = `r ftop_all_aov$anova_table[2,4]`, *p* `r if(ftop_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ftop_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ftop_all_aov$anova_table[3,1]`, `r ftop_all_aov$anova_table[3,2]`) = `r ftop_all_aov$anova_table[3,4]`, *p* `r if(ftop_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ftop_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[3,5])`).

@@

Neither the main effect of Articulation (*F*(`r ptof_all_aov$anova_table[1,1]`, `r ptof_all_aov$anova_table[1,2]`) = `r ptof_all_aov$anova_table[1,4]`, *p* `r if(ptof_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ptof_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[1,5])`) nor Dynamics (*F*(`r ptof_all_aov$anova_table[2,1]`, `r ptof_all_aov$anova_table[2,2]`) = `r ptof_all_aov$anova_table[2,4]`, *p* `r if(ptof_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ptof_all_aov$anova_table[3,1]`, `r ptof_all_aov$anova_table[3,2]`) = `r ptof_all_aov$anova_table[3,4]`, *p* `r if(ptof_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[3,5])`).

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (*Fig \ref{fig:ioi-1}*). Neither the main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* `r if(ioi_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* `r if(ioi_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* `r if(ioi_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`).

>>>>

Neither the main effect of Articulation (*F*(`r ftop_all_aov$anova_table[1,1]`, `r ftop_all_aov$anova_table[1,2]`) = `r ftop_all_aov$anova_table[1,4]`, *p* `r if(ftop_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ftop_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[1,5])`) nor Dynamics (*F*(`r ftop_all_aov$anova_table[2,1]`, `r ftop_all_aov$anova_table[2,2]`) = `r ftop_all_aov$anova_table[2,4]`, *p* `r if(ftop_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ftop_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ftop_all_aov$anova_table[3,1]`, `r ftop_all_aov$anova_table[3,2]`) = `r ftop_all_aov$anova_table[3,4]`, *p* `r if(ftop_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ftop_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[3,5])`).

@@

Neither the main effect of Articulation (*F*(`r ptof_all_aov$anova_table[1,1]`, `r ptof_all_aov$anova_table[1,2]`) = `r ptof_all_aov$anova_table[1,4]`, *p* `r if(ptof_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[1,5])`) nor Dynamics (*F*(`r ptof_all_aov$anova_table[2,1]`, `r ptof_all_aov$anova_table[2,2]`) = `r ptof_all_aov$anova_table[2,4]`, *p* `r if(ptof_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ptof_all_aov$anova_table[3,1]`, `r ptof_all_aov$anova_table[3,2]`) = `r ptof_all_aov$anova_table[3,4]`, *p* `r if(ptof_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[3,5])`).

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (*Fig \ref{fig:ioi-1}*). Neither the main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* `r if(ioi_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* `r if(ioi_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* `r if(ioi_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`).

### 2023-01-31 paper/manuscript.tex
update figure / fix floating pointst
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Neither the main effect of Articulation (\emph{F}(1, 19) = 3.40, \emph{p} = 0.081, \(\eta_G^2\) = 0.012) nor Dynamics (\emph{F}(1, 19) = 1.58, \emph{p} = 0.22, \(\eta_G^2\) = 0.002) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.97, \emph{p} = 0.336, \(\eta_G^2\) = 0.001).

@@

Neither the main effect of Articulation (\emph{F}(1, 19) = 2.25, \emph{p} = 0.150, \(\eta_G^2\) = 0.005) nor Dynamics (\emph{F}(1, 19) = 3.76, \emph{p} = 0.07, \(\eta_G^2\) = 0.004) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.08, \emph{p} = 0.31, \(\eta_G^2\) = 0.001).

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (\emph{Fig \ref{fig:ioi-1}}). Neither the main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.111, \(\eta_G^2\) = 0.010) nor the main effect of Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.086, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002).

>>>>

Neither the main effect of Articulation (\emph{F}(1, 19) = 3.40, \emph{p} = 0.081, \(\eta_G^2\) = 0.012) nor Dynamics (\emph{F}(1, 19) = 1.58, \emph{p} = 0.22, \(\eta_G^2\) = 0.002) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.97, \emph{p} = 0.34, \(\eta_G^2\) = 0.001).

@@

Neither the main effect of Articulation (\emph{F}(1, 19) = 2.25, \emph{p} = 0.15, \(\eta_G^2\) = 0.005) nor Dynamics (\emph{F}(1, 19) = 3.76, \emph{p} = 0.07, \(\eta_G^2\) = 0.004) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.08, \emph{p} = 0.31, \(\eta_G^2\) = 0.001).

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (\emph{Fig \ref{fig:ioi-1}}). Neither the main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.11, \(\eta_G^2\) = 0.010) nor the main effect of Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.086, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002).
